A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-09 src/tex/ms.tex

% To add: Karma Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra

The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks. The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius. The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim1$ Gyr. The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/delay_time_distribution.pdf}
    \caption{Caption.}
    \label{fig:dtd}
\end{figure*}

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfr.pdf}
    \caption{Caption.}
    \label{fig:onezone-sfr}
\end{figure}

@@

Figure \ref{fig:onezone-dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model. The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks. The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal. Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.

\begin{figure*}
    \centering
    \includegraphics{figures/onezone_dtd.pdf}
    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr.}
    \label{fig:onezone-dtd}
\end{figure*}

>>>>

% To add: Carme Gallart (2019) three-infall-ish, Kobayashi metallicity limit for SNe Ia and sub-Chandra

The two-infall model has long been proposed to explain the formation of the Milky Way's thick and thin disks. The infall history of any given region of the disk is described by two successive, exponentially declining bursts, whose timescale may vary as a function of radius. The first infall, which forms the thick disk, has a short timescale, typically on the order of $\sim0.1-1$ Gyr. The second infall forms the thin disk and has a much longer timescale, typically $\sim4-10$ Gyr.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/delay_time_distribution.pdf}
    \caption{The model parameters are fixed at $\tau_1=1$ Gyr, $\tau_2=15$ Gyr, and $\tau_{\rm on}=3.2$ Gyr. Key takeaway: the size of the thin disk loop can be reduced by using an SN Ia DTD with more prompt events. However, this messes up the location of the high-alpha sequence.}
    \label{fig:dtd}
\end{figure*}

Figure \ref{fig:dtd} illustrates the effect of the SN Ia DTD on the abundance predictions by the two-infall model. The fiducial plateau DTD produces the strongest high-$\alpha$ peak as well as the greatest separation between the two low-$\alpha$ peaks. The exponential DTD produces the most stars near Solar [O/Fe], but the low-$\alpha$ sequence is still distinctly bimodal. Finally, the power-law DTD shrinks the low-$\alpha$ loop such that there is only one low-$\alpha$ peak; however, this DTD produces high-$\alpha$ stars at metallicities much lower than observed, as discussed in \citet{dubay_galactic_2024}.

@@

\begin{figure}
    \centering
    \includegraphics{figures/onezone_sfr.pdf}
    \caption{Key takeaway: a fundamental attribute of any two-infall model is a bump in the number of stars on the low-alpha sequence where the abundance track turns over. This is because the star formation rate is near its peak while the rate of chemical evolution has slowed considerably.}
    \label{fig:onezone-sfr}
\end{figure}

@@
